Forecasting the 2024 U.S. Presidential Election

### 2024-10-22 paper/paper.qmd

---
title: "Forecasting the 2024 U.S. Presidential Election"
subtitle: "My subtitle if needed"
author: 
  - Tim Chen
  - Steven Li
  - Tommy Fu
thanks: "Code and data are available at: https://github.com/timchen0326/US_presidential_election_forecast_2024.git."
date: today
date-format: long
abstract: "This paper presents a statistical model for forecasting the outcome of the 2024 U.S. Presidential Election. Using polling data from various sources, we develop multiple linear regression models to predict the percentage of support for the main candidates, Kamala Harris and Donald Trump, in different states. We aggregate these predictions to simulate the Electoral College vote and estimate the likelihood of either candidate winning. Our results suggest that neither candidate currently secures the required 270 electoral votes to win the presidency."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: sentence
---

@@

library(tidyverse)
library(ggplot2)
library(janitor)
library(rstanarm)
library(modelsummary)
library(here)
library(dplyr)
library(knitr)

@@

# Introduction

@@

- Pollster rating: A numerical score reflecting the reliability and historical accuracy of each polling organization.
- Sample size: The number of respondents included in each poll, which influences the poll's margin of error.
- Support percentage: The percentage of respondents expressing support for each candidate.
- State: The U.S. state where the poll was conducted, or in some cases, national-level polling data.

@@

@tbl-overview_data shows a subset of the dataset.

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig.pos: "H"
#| label: fig-support
#| fig-cap: Distribution of Support between Both Candidates

# Create a boxplot showing the distribution of support for each candidate
ggplot(data, aes(x = candidate_name, y = pct, fill = candidate_name)) +
  geom_boxplot() +
  labs(title = "Distribution of Support for Kamala Harris and Donald Trump",
       x = "Candidate",
       y = "Percentage of Support") +
  theme_minimal() +
  theme(legend.position = "none")
```

@@

Some variables were excluded for simplicity and relevance. For example, **"population_full"** and **"answer"** were dropped as they provided redundant or unnecessary information for this analysis. However, key variables like **"pollster"**, **"pollscore"**, **"numeric grade"**, and **"sample size"** were retained because they provide essential insights into the quality and precision of the polls, directly influencing the reliability of the models. These steps ensured the cleaned dataset was ready for analysis, with a focus on the most important predictors of voter support while minimizing extraneous information.

@@

# Perform a simple linear regression with pct as the dependent variable and sample_size as the independent variable
model <- lm(pct ~ sample_size, data = harris_data)

@@

Figure 2 illustrates the relationship between the sample size and support percentage for Kamala Harris.

```{r}
#| echo: false
#| message: false
#| warning: false
# Plot the relationship for Kamala Harris
ggplot(harris_data, aes(x = sample_size, y = pct)) +
  geom_point() +
  geom_smooth(method = "lm", col = "blue") +
  labs(title = "Linear Regression of Percentage vs Sample Size for Kamala Harris",
       x = "Sample Size",
       y = "Percentage")

@@

Figure 3 shows the relationship between the sample size and support percentage for Donald Trump.

```{r}
#| echo: false
#| message: false
#| warning: false

# Plot the relationship for Kamala Harris
ggplot(trump_data, aes(x = sample_size, y = pct)) +
  geom_point() +
  geom_smooth(method = "lm", col = "blue") +
  labs(title = "Linear Regression of Percentage vs Sample Size for Donald Trump",
       x = "Sample Size",
       y = "Percentage")

@@

```{r}
#| echo: false
#| message: false
#| warning: false
mlr_harris_model <- readRDS(here::here(("models/mlr_harris_model.rds")))

# Diagnostic plots for the MLR model
par(mfrow = c(2, 2))
plot(mlr_harris_model)
par(mfrow = c(1, 1))  # Reset plot layout

The results of the MLR for Kamala Harris show that several predictors, including state and pollster rating, significantly impact her predicted percentage of voter support.
These results suggest that voter preferences for Harris vary widely depending on the state and the credibility of the pollster.

@@

```{r}
#| echo: false
#| message: false
#| warning: false
# Load the saved MLR model for Donald Trump
mlr_trump_model <- readRDS(here::here(("models/mlr_trump_model.rds")))

@@

The results for Donald Trump reveal that state-level variations and pollster transparency play a significant role in explaining his level of support.
The model for Trump also passes diagnostic checks, as shown in Figure Y, indicating that the assumptions of linearity, independence, and homoscedasticity are reasonably met.
Check Multicollinearity using Variance Inflation Factor (VIF)

@@

To ensure that the predictors used in both models do not exhibit multicollinearity, we checked the Variance Inflation Factor (VIF) for each predictor.
High VIF values indicate multicollinearity, which can affect the stability and reliability of the model coefficients.

```{r}
#| echo: false
#| message: false
#| warning: false
# Load the car package for VIF
if (!require(car)) install.packages("car")
library(car)

# Check VIF for Kamala Harris model
vif(mlr_harris_model)

# Refine the model by removing less significant predictors (e.g., methodology and transparency_score)
mlr_harris_model_refined <- readRDS(here::here(("models/mlr_harris_model_refined.rds")))

# Summary of the refined Harris model

# Check VIF for the refined model
vif(mlr_harris_model_refined)

# Plot diagnostic plots for the refined model
par(mfrow = c(2, 2))
plot(mlr_harris_model_refined)
par(mfrow = c(1, 1))  # Reset plot layout

Based on the VIF results, we refined the model by removing less significant predictors (such as methodology and transparency_score) to reduce multicollinearity.
This improves the model's accuracy and interpretability.

@@

```{r}
#| echo: false
#| message: false
#| warning: false
# Perform stepwise selection to optimize the Harris model
step_model <- step(mlr_harris_model_refined, direction = "both")

# Plot diagnostic plots for the stepwise model
par(mfrow = c(2, 2))
plot(step_model)
par(mfrow = c(1, 1))  # Reset layout

@@

```{r}
#| echo: false
#| message: false
#| warning: false
# Final models for Harris and Trump
mlr_harris_model_final <- readRDS(here::here(("models/mlr_harris_model_final.rds")))
mlr_trump_model_final <- readRDS(here::here(("models/mlr_trump_model_final.rds")))

@@

```{r}
#| echo: false
#| message: false
#| warning: false
# Define electoral votes for each state (and Washington, D.C.)
electoral_votes <- data.frame(
  state = c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", "Connecticut", "Delaware", "Florida", 
            "Georgia", "Hawaii", "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky", "Louisiana", "Maine", 
            "Maine CD-1", "Maine CD-2", "Maryland", "Massachusetts", "Michigan", "Minnesota", "Mississippi", 
            "Missouri", "Montana", "Nebraska", "Nebraska CD-1", "Nebraska CD-2", "Nebraska CD-3", "Nevada", 
            "New Hampshire", "New Jersey", "New Mexico", "New York", "North Carolina", "North Dakota", "Ohio", 
            "Oklahoma", "Oregon", "Pennsylvania", "Rhode Island", "South Carolina", "South Dakota", "Tennessee", 
            "Texas", "Utah", "Vermont", "Virginia", "Washington", "West Virginia", "Wisconsin", "Wyoming", 
            "District of Columbia"),
  electoral_votes = c(9, 3, 11, 6, 55, 9, 7, 3, 29, 16, 4, 4, 20, 11, 6, 6, 8, 8, 2, 1, 1, 10, 11, 15, 10, 6, 10, 
                      3, 5, 1, 1, 2, 6, 4, 14, 5, 29, 16, 3, 18, 7, 6, 20, 4, 9, 3, 11, 38, 6, 3, 13, 12, 5, 10, 3, 3)
)

@@

Kamala Harris The MLR model for Kamala Harris highlights the importance of state-level factors in determining her support.
The model shows that voter preferences vary significantly across different states, with certain states (e.g., California and Maryland) showing higher support levels, while others (e.g., Indiana and Missouri) show lower support.
Pollster reliability, captured through numeric grades and transparency scores, also plays an important role, suggesting that voters may respond differently based on the credibility of the pollster.

@@

Poll Reliability and Sampling Bias: The accuracy of the predictions depends heavily on the quality of the polling data.
Although the model accounts for pollster ratings, polling methodologies can still introduce biases, particularly in states with limited polling data.
Sampling errors and non-response biases could skew the results, especially in smaller states or regions with inconsistent polling coverage.

Static Prediction: The model provides a static snapshot of voter support based on current polling data, which may not capture the dynamic nature of voter preferences over time.
As election day approaches, voter preferences may shift due to campaign events, debates, or other external factors.
Without time-series data, the model may fail to account for these trends.

Unaccounted Variables: Although the model includes important predictors like state, pollscore, and transparency score, other potentially influential factors, such as economic conditions, campaign spending, and voter turnout, are not included in the analysis.
These unaccounted variables may introduce inaccuracies in the final predictions.
## Future Research Directions Future work could improve upon this analysis by addressing some of the limitations mentioned above.
For instance, incorporating time-series data could allow the model to capture how voter preferences evolve in response to external factors such as campaign events, economic developments, and political endorsements.
A dynamic forecasting model that updates predictions as new polls are released would provide more timely and accurate forecasts.

@@

# Appendix {.unnumbered}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check.
This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior.
This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

## Diagnostics

@fig-stanareyouokay-1 is a trace plot.
It shows...
This suggests...

@fig-stanareyouokay-2 is a Rhat plot.
It shows...
This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

@@

#References

>>>>

---
title: "Forecasting the 2024 U.S. Presidential Election"
subtitle: "My subtitle if needed"
author: 
  - Tim Chen
  - Steven Li
  - Tommy Fu
thanks: "Code and data are available at: https://github.com/timchen0326/US_presidential_election_forecast_2024.git"
date: today
date-format: long
abstract: "This paper presents a statistical model for forecasting the outcome of the 2024 U.S. Presidential Election. Using polling data from various sources, we develop multiple linear regression models to predict the percentage of support for the main candidates, Kamala Harris and Donald Trump, in different states. We aggregate these predictions to simulate the Electoral College vote and estimate the likelihood of either candidate winning. Our results suggest that neither candidate currently secures the required 270 electoral votes to win the presidency."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: sentence
---

@@

library(tidyverse)
library(ggplot2)
library(janitor)
library(modelsummary)
library(here)
library(dplyr)
library(knitr)
library(car)

@@

\newpage
# Introduction

@@

- **Pollster rating:** A numerical score reflecting the reliability and historical accuracy of each polling organization.
- **Sample size:** The number of respondents included in each poll, which influences the poll's margin of error.
- **Support percentage:** The percentage of respondents expressing support for each candidate.
- **State:** The U.S. state where the poll was conducted, or in some cases, national-level polling data.

@@

@tbl-overview_data shows a sample of the dataset.

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig.pos: "H"
#| label: fig-support
#| fig-cap: Distribution of Support for Kamala Harris and Donald Trump

# Create a boxplot showing the distribution of support for each candidate
ggplot(data, aes(x = candidate_name, y = pct, fill = candidate_name)) +
  geom_boxplot() +
  labs(x = "Candidate",
       y = "Percentage of Support") +
  theme_minimal() +
  theme(legend.position = "none")
```

@@

Some variables were excluded for simplicity and relevance. For example, **'population_full'** and **'answer'** were dropped as they provided redundant or unnecessary information for this analysis. However, key variables like **'pollster'**, **'pollscore'**, **'numeric grade'**, and **'sample size'** were retained because they provide essential insights into the quality and precision of the polls, directly influencing the reliability of the models. These steps ensured the cleaned dataset was ready for analysis, with a focus on the most important predictors of voter support while minimizing extraneous information.

@@

# Perform a simple linear regression with pct as the dependent variable and sample_size as the independent variable
model <- lm(pct ~ sample_size, data = harris_data)
```

@@

@fig-harris-samplesize-supportpct illustrates the relationship between the sample size and support percentage for Kamala Harris.

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-harris-samplesize-supportpct
#| fig-cap: Linear Regression of Percentage vs Sample Size for Kamala Harris

# Plot the relationship for Kamala Harris
ggplot(harris_data, aes(x = sample_size, y = pct)) +
  geom_point() +
  geom_smooth(method = "lm", col = "blue") +
  labs(x = "Sample Size",
       y = "Percentage")
```

@@

@fig-trump-samplesize-supportpct shows the relationship between the sample size and support percentage for Donald Trump.

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-trump-samplesize-supportpct
#| fig-cap: Linear Regression of Percentage vs Sample Size for Donald Trump

# Plot the relationship for Trump
ggplot(trump_data, aes(x = sample_size, y = pct)) +
  geom_point() +
  geom_smooth(method = "lm", col = "blue") +
  labs(x = "Sample Size",
       y = "Percentage")

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-mlr-harris
#| fig-cap: Multi-Linear Regression model for Kamala Harris

mlr_harris_model <- readRDS(here::here(("models/mlr_harris_model.rds")))

# Diagnostic plots for the MLR model
par(mfrow = c(2, 2))
plot(mlr_harris_model)
par(mfrow = c(1, 1))  # Reset plot layout
```

The results in @fig-mlr-harris show that several predictors, including state and pollster rating, significantly impact her predicted percentage of voter support.
These results suggest that voter preferences for Harris vary widely depending on the state and the credibility of the pollster.

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-mlr-trump
#| fig-cap: Multi-Linear Regression model for Donald Trump

# Load the saved MLR model for Donald Trump
mlr_trump_model <- readRDS(here::here(("models/mlr_trump_model.rds")))

@@

The results for Donald Trump in @fig-mlr-trump reveal that state-level variations and pollster transparency play a significant role in explaining his level of support.
The model for Trump also passes diagnostic checks, as shown in Figure Y, indicating that the assumptions of linearity, independence, and homoscedasticity are reasonably met.
Check Multi-collinearity using Variance Inflation Factor (VIF)

@@

To ensure that the predictors used in both models do not exhibit multi-collinearity, we checked the Variance Inflation Factor (VIF) for each predictor. High VIF values indicate multi-collinearity, which can affect the stability and reliability of the model coefficients.

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: tbl-harris-vif
#| tbl-cap: Harris MLR model Variance Inflation Factor (VIF)

# Check VIF for Kamala Harris model
kable(vif(mlr_harris_model), digits=3)
```

Based on the VIF results in @tbl-harris-vif, we refined the model by removing less significant predictors (such as methodology and transparency_score) to reduce multi-collinearity.This improves the model's accuracy and interpretability.

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-harris-vif
#| fig-cap: Harris Refined Multi-Linear Regression Model

# Refine the model by removing less significant predictors 
# (e.g., methodology and transparency_score)
mlr_harris_model_refined <- readRDS(here::here(("models/mlr_harris_model_refined.rds")))

# Plot diagnostic plots for the refined model
par(mfrow = c(2, 2))
plot(mlr_harris_model_refined)
par(mfrow = c(1, 1))  # Reset plot layout
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: tbl-harris-refined-vif
#| tbl-cap: Harris Refined MLR model Variance Inflation Factor (VIF)

# Refine the model by removing less significant predictors 
# (e.g., methodology and transparency_score)

# Check VIF for the refined model
kable(vif(mlr_harris_model_refined), digits=3)
```

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-bbb
#| fig-cap: bbb

# Perform stepwise selection to optimize the Harris model
step_model <- step(mlr_harris_model_refined, direction = "both", trace=0)

# Plot diagnostic plots for the stepwise model
par(mfrow = c(2, 2))
plot(step_model)
par(mfrow = c(1, 1))  # Reset layout
```

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-ccc
#| fig-cap: ccc

# Final models for Harris and Trump
mlr_harris_model_final <- readRDS(here::here(("models/mlr_harris_model_final.rds")))
mlr_trump_model_final <- readRDS(here::here(("models/mlr_trump_model_final.rds")))

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-ddd
#| fig-cap: ddd

# Define electoral votes for each state (and Washington, D.C.)
electoral_votes <- data.frame(
  state = c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", "Connecticut", "Delaware", "Florida", 
            "Georgia", "Hawaii", "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky", "Louisiana", "Maine", 
            "Maine CD-1", "Maine CD-2", "Maryland", "Massachusetts", "Michigan", "Minnesota", "Mississippi", 
            "Missouri", "Montana", "Nebraska", "Nebraska CD-1", "Nebraska CD-2", "Nebraska CD-3", "Nevada", 
            "New Hampshire", "New Jersey", "New Mexico", "New York", "North Carolina", "North Dakota", "Ohio", 
            "Oklahoma", "Oregon", "Pennsylvania", "Rhode Island", "South Carolina", "South Dakota", "Tennessee", 
            "Texas", "Utah", "Vermont", "Virginia", "Washington", "West Virginia", "Wisconsin", "Wyoming", 
            "District of Columbia"),
  electoral_votes = c(9, 3, 11, 6, 55, 9, 7, 3, 29, 16, 4, 4, 20, 11, 6, 6, 8, 8, 2, 1, 1, 10, 11, 15, 10, 6, 10, 
                      3, 5, 1, 1, 2, 6, 4, 14, 5, 29, 16, 3, 18, 7, 6, 20, 4, 9, 3, 11, 38, 6, 3, 13, 12, 5, 10, 3, 3)
)

@@

The MLR model for Kamala Harris highlights the importance of state-level factors in determining her support.
The model shows that voter preferences vary significantly across different states, with certain states (e.g., California and Maryland) showing higher support levels, while others (e.g., Indiana and Missouri) show lower support.
Pollster reliability, captured through numeric grades and transparency scores, also plays an important role, suggesting that voters may respond differently based on the credibility of the pollster.

@@

- **Poll Reliability and Sampling Bias:** The accuracy of the predictions depends heavily on the quality of the polling data.
Although the model accounts for pollster ratings, polling methodologies can still introduce biases, particularly in states with limited polling data.
Sampling errors and non-response biases could skew the results, especially in smaller states or regions with inconsistent polling coverage.
- **Static Prediction:** The model provides a static snapshot of voter support based on current polling data, which may not capture the dynamic nature of voter preferences over time. As election day approaches, voter preferences may shift due to campaign events, debates, or other external factors.
Without time-series data, the model may fail to account for these trends.
- **Unaccounted Variables:** Although the model includes important predictors like state, pollscore, and transparency score, other potentially influential factors, such as economic conditions, campaign spending, and voter turnout, are not included in the analysis.These unaccounted variables may introduce inaccuracies in the final predictions.

## Future Research 
Directions Future work could improve upon this analysis by addressing some of the limitations mentioned above. For instance, incorporating time-series data could allow the model to capture how voter preferences evolve in response to external factors such as campaign events, economic developments, and political endorsements.
A dynamic forecasting model that updates predictions as new polls are released would provide more timely and accurate forecasts.

@@

# Appendix

## YouGov Pollster Methodology Overview and Evaluation
YouGov conducts online surveys through their proprietary panel of U.S. adults, using nonprobability sampling methods combined with sophisticated weighting procedures to achieve representative results. Their approach balances speed and cost-effectiveness with statistical rigor through careful sample selection and data quality controls.

### Survey Population and Sampling
YouGov's target population typically comprises all U.S. adults or adult citizens, with their sampling frame consisting of their opt-in online panel covering approximately 95% of Americans. For general population surveys, they aim for 1,000-2,000 respondents, selected based on demographic and political characteristics to match the target population.

### Panel Recruitment and Participation
Panel members are recruited through advertising and website partnerships, with surveys offered in multiple languages including Spanish to ensure broad representation. Participants receive points exchangeable for small monetary rewards, though many report being motivated by the desire to contribute to research.

### Quality Control
YouGov employs several measures to maintain data quality:

- Verification of panelist identity through email and IP checks
- Response quality surveys to gauge reliability
- Monitoring of response times and patterns
- Removal of respondents who fail quality checks
- Question randomization to reduce bias

### Non-response and Weighting
To address potential biases, YouGov applies statistical weighting based on demographics (age, gender, race, education) and political factors (voting behavior, party identification). Their weighting process considers multiple characteristics simultaneously to better reflect real-world demographic intersections.

### Strengths and Limitations
The methodology's primary strengths include rapid data collection, cost-effectiveness, and the ability to track opinions over time. However, the nonprobability sampling approach may introduce biases, and the online-only format could underrepresent certain populations. While weighting helps address these limitations, it cannot fully account for all potential sources of bias.

## Idealized Survey Methodology
This idealized survey methodology outlines a comprehensive plan for forecasting the US presidential election within a budget of $100,000. The approach is designed to be statistically sound, practical, and capable of accurately predicting election outcomes by considering both the popular vote and electoral college implications.

### Sampling Strategy
The target population for this survey is eligible voters across the United States who are likely to participate in the upcoming presidential election. To achieve a representative sample:

- **Sampling Frame:** Utilize a combination of registered voter lists and demographic data from reputable sources such as the US Census Bureau.
- **Sampling Method:** Implement stratified random sampling to ensure representation across key demographics, including age, gender, race, education level, and geographic location.
- **Sample Size Calculation:** Aim for a sample size of approximately 10,000 respondents to achieve a margin of error of ±1% at a 95% confidence level.
- **Geographical Distribution:** Allocate samples proportionally across all 50 states and the District of Columbia, with oversampling in swing states to better predict electoral college outcomes.
- **Addressing Sampling Biases:** Apply weighting adjustments to account for underrepresented groups and ensure that the sample mirrors the overall voter population.

### Recruitment Plan
To recruit respondents effectively, we will leverage online panels, social media advertising, and partnerships with community organizations to reach a diverse audience. Offering modest incentives, such as $5 digital gift cards, encourages participation while managing costs. Quota sampling within strata maintains demographic balance, and follow-up reminders along with mobile-friendly survey formats help reduce non-response bias. The data collection will occur over a two-week period to capture timely opinions without introducing temporal biases.

### Survey Design Elements
The survey is crafted to elicit accurate and meaningful responses:

- **Question Types and Formats:** Use a mix of closed-ended questions and multiple-choice options for clarity and ease of analysis.
- **Response Options:** Include balanced and neutral response choices, with options for "Undecided" or "Prefer not to say."
- **Question Order and Flow:** Begin with general questions to build rapport, followed by more specific vote intention queries, and conclude with demographic questions.
- **Demographic Information:** Collect data on age, gender, race, education, income, and geographic location.
- **Political Affiliation and History:** Ask about party affiliation, past voting behavior, and political engagement.
- **Likely Voter Screens:** Include questions to gauge voting likelihood, such as past voting frequency and intention to vote in the upcoming election.
- **Vote Intention Questions:** Directly ask which candidate the respondent intends to vote for, ensuring confidentiality and anonymity.

### Quality Control
To maintain data integrity, we implement several quality control measures. Real-time validation checks within the survey prevent inconsistent or illogical responses. Attention-check questions identify disengaged respondents. We use unique survey links and track IP addresses to prevent duplicate submissions, while CAPTCHA verification deters automated responses. Incomplete or suspicious responses are excluded during data cleaning to ensure the final dataset is robust and reliable.

### Data Processing
These data processing steps will be taken to ensure accurate analysis:

- **Weighting Methodology:** Adjust survey results using weighting factors based on demographic proportions in the voting population.
- **Handling Missing Data:** Employ imputation techniques or exclude cases with significant missing information.
- **Outlier Detection:** Identify and review outliers that may skew results, determining whether to retain or discard them.
- **Response Validation:** Cross-check responses for consistency and plausibility.
- **Poll Aggregation Approach:** Combine survey data with other reputable polls using meta-analytic techniques to enhance prediction accuracy.

### Budget Allocation
A budget allocation of $100,000 ensures all aspects are adequately funded:

- **Recruitment Costs:** $40,000 for advertising and partnerships to reach potential respondents.
- **Incentive Payments:** \$50,000 allocated for participant incentives ($5 x 10,000 respondents).
- **Survey Platform Fees:** $2,000 for premium features on a survey platform like Google Forms or an equivalent.
- **Data Analysis Tools:** $3,000 for statistical software licenses and data processing tools.
- **Quality Control Measures:** $3,000 for implementing validation systems and CAPTCHA services.
- **Administrative Costs:** $2,000 for project management and miscellaneous expenses.

### Conclusion
This methodology presents a feasible and thorough plan to forecast the US presidential election within the specified budget. By adhering to best practices in survey design and execution, and by carefully considering both the popular vote and electoral college implications, the survey aims to provide accurate and reliable insights into voter intentions.

@@

# References
